### 2015-07-10 narrative/qos.tex
removed priorty portion.
added a sentence to charging model

Another essential component of performance isolation is the \emph{charging
model} that determines which task(s) should be charged how much for a request.
Performance isolation is implemented by the charging model by ensuring that
task performance only depends on its reservation and its workload behavior (but
not on other workloads in the system). Each task has a budget based on its
reservation and spends it based on the cost of each request determined by the
charging model. A charging model determines the cost based on the utilization
model and the interactions a request can have with other requests (e.g. a
random request to spinning media interrupting a stream of sequential requests).

@@

As stated in the introduction, we seek to make a storage stack that works with
the user. Towards that end, we must incorporate data attributes into this
process. For example, particularly for a capability run, the storage system
should give (on a user by user basis), higher priority to data subset tagged with high importance to stay in fast
storage tier
administrators.
 It should also store the highest value data possible given
the performance requirement. Ideally, the storage system will store the raw
data at full fidelity. When this tier approaches capacity, data should migrate
not just based on age, but also based on this value. One area of research will be in
trying to see if we can retain some guarantees of QoS while giving some high-profile users
greater SSIO a higher {\bf priority} than other users on the system. We realize that this makes
it very difficult to main overall system QoS, but we will investigate techniques when one
user is running on the majority of the exascale resource and we can allow them to lock out other SSIO
request during small periods of time during the lifetime of their exascale simulation.

>>>>

Another essential component of performance isolation is the \emph{charging
model} that determines which task(s) should be charged how much for a request.
Performance isolation is implemented by the charging model by ensuring that
task performance only depends on its reservation and its workload behavior (but
not on other workloads in the system). Each task has a budget based on its
reservation and spends it based on the cost of each request determined by the
charging model. A charging model determines the cost based on the utilization
model and the interactions a request can have with other requests (e.g. a
random request to spinning media interrupting a stream of sequential
requests). Thus users with a higher allocation can still meet their higher
requirements for I/O, without violating the gurantees given to other users.

@@

% As stated in the introduction, we seek to make a storage stack that works with
% the user. Towards that end, we must incorporate data attributes into this
% process. For example, particularly for a capability run, the storage system
% should give (on a user by user basis), higher priority to data subset tagged with high importance to stay in fast
% storage tier
% administrators.
%  It should also store the highest value data possible given
% the performance requirement. Ideally, the storage system will store the raw
% data at full fidelity. 
% When this tier approaches capacity, data should migrate
% not just based on age, but also based on this value. One area of research will be in
% trying to see if we can retain some guarantees of QoS while providing
% policies that can govern admissio
% greater SSIO a higher {\bf priority} than other users on the system. 
% We realize that this makes
% it very difficult to main overall system QoS, but we will investigate techniques when one
% user is running on the majority of the exascale resource and we can allow them to lock out other SSIO
% request during small periods of time during the lifetime of their exascale simulation.
